\bf Faster Neural Machine Translation Inference

### 2018-02-06 fast-beam/fast-beam.tex
fast beam paper

It has been shown ~\citep{koehn-knowles:2017:NMT} that using beam search to use the n-best number of classes, rather than just the best class, improves translation quality, up to a point. Unlike the 1-best case, however, the softmax calculation cannot be skipped as the denominator differs for each input.

>>>>

It has been noted by ~\citep{koehn-knowles:2017:NMT} and others that using n-best number of classes, rather than just the best class, improves translation quality. Unlike the 1-best case, however, the softmax calculation cannot be skipped as the denominator differs for each input.
